\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{charter}

% Linkedin symbol
\usepackage{fontawesome}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% indent
\usepackage{indentfirst}
%\usepackage{textcomp}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-45pt}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\Large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemtwo}[2]{
  \item[]\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[5]{
    \setlength{\itemindent}{-9pt}
    \item[]
    \begin{tabular*}{.99\textwidth}{p{0.99\textwidth}}
      {\textbf{{#1}}}{{#2}} \hfill{\small{#3}} \\
      {\small{#4}} \hfill{\small{#5}} \\
    \end{tabular*}
    \vspace{-7pt}
}

\newcommand{\resumeSubItem}[2]{\vspace{-2pt}\resumeItem{#1}{#2}\vspace{-2pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-14pt}}

\newcommand{\resumeItemListStart}{\vspace{0pt}\begin{itemize}[leftmargin=*]\setlength{\itemindent}{-9pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
%\begin{tabular}{ p{370pt}  l}
 % \textbf{{\Large Ziwei Cheng}} & Email : %ziweic@andrew.cmu.edu \vspace{3pt}\\
 % \textit{Actively seeking for software engineer %internship in summer 2020} & Mobile : (412)-897-4829 %%\textit{www.linkedin.com/in/ziwei-cheng} &
  %Location : Pittsburgh, PA
%\end{tabular}
\begin{center}
  
  \textbf{{\LARGE Ziwei Cheng}}
  
  %\vspace{3pt}
  
  %Actively seeking internship opportunities in summer 2020.
  \vspace{2pt}
  
  \faEnvelope\ \href{mailto://ziweic@cmu.edu}{ziweic@cmu.edu} \hspace{1pt}
  \faPhone\ (412) 897-4829 \hspace{1pt} 
%   \faLinkedinSquare\ \href{https://www.linkedin.com/in/ziwei-cheng}{ziwei-cheng} \hspace{1pt} 
  \faGithub\ \href{https://www.github.com/zw-cheng}{zw-cheng} \hspace{1pt} 
  \faHome\ Sunnyvale, CA
  
  
  \vspace{-10pt}
\end{center}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
  \resumeSubheading{Carnegie Mellon University}{, Information Networking Institute}{Aug. 2019 - May 2021}{\textbf{}Master of Science in Information Technology - Information Security, GPA 3.5/4.0}{}
      \resumeItemListStart
      \resumeItem{}{Coursework: Distributed Systems, Parallel Computer Architecture \& Programming, Advanced Real-World Networks, Computer Systems, Information Security, Web Application Development}
      \resumeItemListEnd
    \resumeSubheading
      {University of Science and Technology Beijing}{, School of Computer Engineering}{Aug. 2015 - June 2019}{\textbf{}Bachelor of Engineering in Information Security, GPA 3.7/4.0}{}
      \resumeItemListStart
      \resumeItem{}{Coursework: Computer Networks, Operating Systems, Computer Architecture, Database Systems, Data Structures}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  

%-----------EXPERIENCE-----------------
\section{Employment}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Apple}{}{May 2020 - Aug. 2020}
      {\textbf{Software Engineer Intern}}{}
      \resumeItemListStart
        \resumeItem{}
          {Developed \textbf{TCP} time sequence graph for fast network troubleshooting, integrated into an internal tool on macOS }
          \resumeItem{}
          {Parsed out data from TCP/IP headers and visualized it to show various network events in TCP connection }
        \resumeItem{}
          {Implemented basic elements of coordinate system from scratch using \textbf{Swift} and CoreGraphics}
        % \resumeItem{}
        %   {Optimized the rendering speed; }
     \resumeItemListEnd
     
    \resumeSubheading
      {Chinese Academy of Sciences}{}{July 2018 - Jan. 2019}
      {\textbf{Software Engineer Intern}}{}
      \resumeItemListStart
        \resumeItem{}
         {Developed a network scanning tool with \textbf{Go} language, supported more than \textbf{60} protocols}
         \resumeItem{}
          {Detected hundreds of insecure devices using the tool, and produced reports for security auditing purpose}
        \resumeItem{}
          {Boosted scanning speed to \textbf{2x faster} than Nmap by executing concurrent instances using goroutine}


        % \resumeItem{}
        %  {Discovered and exploited \textbf{five} protocol vulnerabilities, thus protected \textbf{hundreds of devices}. For example, reverse-}
        % \resumeItemtwo{}
        %  {engineered password reset process and sent constructed packets by \textbf{Python} to access camera video}
     \resumeItemListEnd

    \resumeSubheading
      {Lenovo}{}{July 2017 - Sept. 2017}
      {\textbf{Product Engineer Intern}}{}
      \resumeItemListStart
        \resumeItem{}
        {Conducted market research for Lenovo SmartVest, a wireless smart ECG wear, to enable future investment}
        \resumeItem{}
        {Predicted long-term product price by regression modelling \textbf{30,000 user data} with \textbf{Python} to determine the price strategy}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
  
  \resumeSubheading
      {Transparent Remote File Operation System}{}{Jan. 2020 - Feb. 2020}
      {}{} \vspace{-20pt}
      \resumeItemListStart
        \resumeItem{}
        {Built an RPC (Remote Procedure Calls) system to access remote services in \textbf{C}, including a server and client stub library}
        % through interposing RPC stubs in C library}
        \resumeItem{}
        {Designed and implemented serialization protocol, sending and reconstructing recursive data structures over TCP/IP}
        \resumeItem{}
        {Developed multi-client server for concurrent file operation requests, such as open, read, write, lseek, stat, etc.}
      \resumeItemListEnd
      
      \resumeSubheading
      {Transparent Remote File Operation System}{}{Jan. 2020 - Feb. 2020}
      {}{} \vspace{-20pt}
      \resumeItemListStart
        \resumeItem{}
        {Built an RPC (Remote Procedure Calls) system to access remote services in \textbf{C}, including a server and client stub library}
        % through interposing RPC stubs in C library}
        \resumeItem{}
        {Designed and implemented serialization protocol, sending and reconstructing recursive data structures over TCP/IP}
        \resumeItem{}
        {Developed multi-client server for concurrent file operation requests, such as open, read, write, lseek, stat, etc.}
      \resumeItemListEnd
      
      \resumeSubheading
      {Caching Web Proxy Server}{}{Nov. 2019 - Dec. 2019}
      {}{} \vspace{-20pt}
      \resumeItemListStart
        \resumeItem{}
        {Built an HTTP1.0/1.1 web proxy in \textbf{C}; processed multiple requests in parallel with POSIX threads}
        \resumeItem{}
        {Implemented LRU cache to accelerate service requests, shared resources are protected by reader/writer semaphore lock}
      \resumeItemListEnd
      
      \resumeSubheading
      {Object Detection System Based on Coexistence Relationship Learning }{}{Feb. 2019 - June 2019}
      {}{} \vspace{-20pt}
      \resumeItemListStart
          \resumeItem{}
          {Proposed a model to improve performance for multi-class object detection by learning coexistence feature}
          \resumeItem{}
          {Built the proposed network using \textbf{Python} and \textbf{Tensorflow} with attention mechanism}
          \resumeItem{}
          {Outperformed Faster R-CNN framework by \textbf{1.1\%} on precision, evaluated on MS-COCO dataset}
      \resumeItemListEnd
     
      
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \resumeSubItem{Languages: }{\textbf{Go}, \textbf{C++}, C, Python, Swift, Java, Bash, MySQL, PHP}
   \resumeSubItem{Tools: }{Linux, Git, Azure, Django, Wireshark, LaTeX}
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}

      \resumeSubheading
      {Dynamic Memory Allocator}{}{Oct. 2019}
      {}{} \vspace{-20pt}
      \resumeItemListStart
        \resumeItem{}
        {Implemented high-performance dynamic storage allocator for \textbf{C} programs, including malloc, free, realloc, and calloc}
        \resumeItem{}
        {Designed segregated free list with FIFO and first fit policy, minimized fragmentation and improved search efficiency }
        \resumeItem{}
        {Improved space utilization and throughput by eliminating footer, decreasing minimum block size, etc.}
      \resumeItemListEnd